---
title: "Historical Presidential Election Polls"
author: "Dan Rosenfeld"
date: "8/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I wanted to take a look at historical presidential election poll data from Fivethirtyeight.
https://fivethirtyeight.com/features/how-to-read-2020-polls-like-a-pro/

Clearly, there are many considerations to take into account when analyzing polls, though I want to know if quantity necessarily equals quality. I am curious about the total number of polls taken in each presidential cycle, and if the modern political age is different in this regard from the past.

```{r cycles}
## Referencing code from Armenoush Aslanian-Persico 2016 assignment https://rpubs.com/aapsps/151233
x <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/polls/pres_pollaverages_1968-2016.csv")

years_analyzed <- unique(x$cycle)
years_analyzed
```

## Including Plots

In the histogram below, you can clearly see that the number of polls in the database greatly increased with the 1992 presidential election.

```{r hist}
hist(x$cycle)
```

Further analysis is required to determine if more polling has necessarily led to more accurate polling. As my skill with R increases I want to compare this historical polling data to actual election results, to see if quantity does have any relationship to quality. 