---
title: "Assignment 7"
author: "Dan Rosenfeld"
date: "10/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 7

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

I'll begin by selecting three of my favorite books and ascertaining their title, author(s), publication year, and the year they were originally published. First I will import these variables in a JSON file, then XML, and finally an HTML table.

</div> \hfill\break

```{r Importing Libraries, echo=FALSE}
library(tidyverse)
library(stringr)
library(rjson)
library(XML)
library(methods)
library(htmltab)
library(RCurl)
library(rlist)
```

## Importing books as a JSON

```{r JSON}
# I'll begin by importing three of my favorite books, including one that has multiple authors
# 1. Candide by Voltaire
# 2. Metamorphosis by Franz Kafka
# 3. R for Data Science: Import, Tidy, Transform, Visualize, and Model Data by Hadley Wickham & Garrett Grolemund

# I wrote out the JSON file using the Sublime text editor and placed it on Github at #https://raw.githubusercontent.com/DanielRosenfeld/CUNYMSDataScience/master/Assignment7Books.json
# I referenced the tutorial at https://www.tutorialspoint.com/r/r_json_files.htm , shared by Cassie Boylan on our class slack channel.

booksjsonurl <- url("https://raw.githubusercontent.com/DanielRosenfeld/CUNYMSDataScience/master/Assignment7Books.json")

booksjson <- fromJSON(file = booksjsonurl)

(books_json_data_frame <- as.data.frame(booksjson))

```

## Importing books as XML


```{r XML}
# Next I'll import the same data as an XML file.
# I also wrote it out in the Sublime text editor.
# I used another tutorial that Cassie Boylan shared, at https://www.tutorialspoint.com/r/r_xml_files.htm .
# I uploaded the file to Github at https://raw.githubusercontent.com/DanielRosenfeld/CUNYMSDataScience/master/Assignment7BooksXML.xml


xmlurl <- getURL("https://raw.githubusercontent.com/DanielRosenfeld/CUNYMSDataScience/master/Assignment7BooksXML.xml",.opts = list(ssl.verifypeer = FALSE) )

# Couldn't get this file parsed out as a table.
(booksxml <- xmlParse(file = xmlurl))
```

```{r html}
# Finally I'll load the html table that I created of the same books in Sublime text editor.
htmlurl <- getURL("https://raw.githubusercontent.com/DanielRosenfeld/CUNYMSDataScience/master/Assignment7Books.html",.opts = list(ssl.verifypeer = FALSE) )
htmlbooks <- readHTMLTable(htmlurl)
htmlbooks
```
